The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-14 paper.tex
update

\item The Galactic bubbles are nearly symmetric about the Galactic plane albeit the jet is at an angle $45^{\circ}$\
      with respect to the disc normal.
\item The randomness of clumpy disk has a insignificant impact on the overall dynamic of the Galactic bubbles.\
      The ambient stratification facilitates the eROSITA bubbles elongation significantly.
      The development of the inverse shocks are always associated with the dense disc.
\item The edge of the eROSITA bubbles is a forward shock,\
      originally driven by a oblique bipolar jets emanating from the GC 12.39 million years ago,\
      and significantly stretched by the stratified atmosphere afterwards.
\item Followed by the forward shock is a contact discontinuity,\
      which we interpret as the edge of the \textit{Fermi} bubbles.\
      The nature of the \textit{Fermi} bubbles are essentially a turbulent and high-temperature ($\sim1$ keV)\
      plasma in pressure balance with the external medium. Associated with the Galactic magnetic field\
      will lead to the stochastic acceleration of CRe, and probably balanced with the IC and synchrotron cooling.\
      We will investigate the competition between CRe acceleration and radiative cooling in a future work.
\item The same leptotonic CRe can simultaneously\
      account for the \textit{Fermi} bubbles and haze emission suggested that\
      they have their origin around the GC,\
      and that the magnetic fields within the bubbles are close to the exponentially distributed\
      Galactic magnetic field.
\end{itemize}

Over the past few years, there have been numerous efforts,\
both observational and theoretical, to uncover the nature of the Galactic bubbles.

Spektr-RG \citep{Sunyaev2021} and eROSITA \citep{Predehl2021}

@@

We therefore suggest that the Fermi bubbles and the eROSITA structure are physically related,\
as suggested by \citet{Predehl2020}.

Our discovery confirms the previously suggested common origin of the two objects \citep{Sofue2000,Kataoka2018}

The broad agreement between simulated and observed X-ray map provides supporting\
evidence for the inclined jet scenario,
\section*{Data Availability}
The data underlying this article are available in the article and in its online supplementary material.

>>>>

\item The Galactic bubbles are nearly symmetric about the Galactic plane albeit the jet is at an angle $45^{\circ}$\
      with respect to the disc normal.\
      The broad agreement between simulated and observed mutiwavelength features\
      provides supporting evidence for the inclined jet scenario, and also\
      releases the caveat given by earlier simulation-based studies:\
      the jets shall be vertical to the disc normal.
\item The randomness of clumpy disk has a insignificant impact on the overall dynamic of the Galactic bubbles.\
      The ambient stratification facilitates the eROSITA bubbles elongation significantly.
      The development of the inverse shocks are always associated with the dense disc.
\item The edge of the eROSITA bubbles is a forward shock,\
      originally driven by a oblique bipolar jets emanating from the GC 12.39 million years ago,\
      and significantly stretched by the stratified atmosphere afterwards.
\item Followed by the forward shock is a contact discontinuity,\
      which we interpret as the edge of the \textit{Fermi} bubbles.\
      The nature of the \textit{Fermi} bubbles are essentially a turbulent and high-temperature ($\sim1$ keV)\
      plasma in pressure balance with the external medium. Associated with the Galactic magnetic field\
      will lead to the stochastic acceleration of CRe, and probably balanced with the IC and synchrotron cooling.\
      We will investigate the competition between CRe acceleration and radiative cooling in a future work.
\item The same leptotonic CRe can simultaneously\
      account for the \textit{Fermi} bubbles and haze emission suggested that\
      they are physically related around the GC,\
      and that the magnetic fields within the bubbles are close to the exponentially distributed\
      Galactic magnetic field.
\end{itemize}

%Over the past few years, there have been numerous efforts,\
%both observational and theoretical, to uncover the nature of the Galactic bubbles.
%
%
%Spektr-RG \citep{Sunyaev2021} and eROSITA \citep{Predehl2021}

@@

%We therefore suggest that the Fermi bubbles and the eROSITA structure are physically related,\
%as suggested by \citet{Predehl2020}.

%Our discovery confirms the previously suggested common origin of the two objects \citep{Sofue2000,Kataoka2018}

\section*{Data Availability}
The data underlying this article are available in the article and in its online supplementary material.
